\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont How innovations thrive in GRASS GIS }} }

### 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
author list and typos
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70654 15284696-431f-4ddb-bdfa-cd5b030d7da7

\newlength{\grasslogoheight}
\setlength{\grasslogoheight}{0.08\textheight}
\newlength{\instlogoheight}
\setlength{\instlogoheight}{0.35\grasslogoheight}

\titlegraphic{
\begin{minipage}{0.3\linewidth}
\includegraphics[height=\grasslogoheight]{grass}
\hspace{2em}
\includegraphics[height=\grasslogoheight]{osgeo_project}
\end{minipage}
\hfill
\begin{minipage}{0.15\linewidth}
\setlength{\baselineskip}{120pt}
\begin{flushright}
\includegraphics[height=\instlogoheight]{ncstate}
~
\includegraphics[height=\instlogoheight]{ctu_prague}
~
\includegraphics[height=\instlogoheight]{dwd}
~
\includegraphics[height=\instlogoheight]{eurac}
~
\includegraphics[height=\instlogoheight]{mundialis}
~
\includegraphics[height=\instlogoheight]{fem_cri}
~
\includegraphics[height=\instlogoheight]{ec_jrc}
\end{flushright}
\end{minipage}
\vspace{-\grasslogoheight}
}

@@

\author{
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Yann Chemin,
Martin Landa\inst{2},
Thomas Leppelt\inst{3},
Pietro Zambelli\inst{4},
Luca Delucchi\inst{5},
Margherita Di Leo\inst{6}
S\"{o}ren Gebbert,
Markus Neteler\inst{7},
}
\institute{
\instlist{1}NCSU, USA;
\instlist{2}FCE CTU in Prague, Czech Republic;
\instlist{3}Deutscher Wetterdienst, Germany;
\instlist{4}EURAC, Italy;
\instlist{5}CRI, FEM, Italy;
\instlist{6}EC-JRC, Italy
\instlist{7}mundialis GmbH \& Co. KG, Germany;
}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{google}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
Initial development of \gmodule{i.segement} module as well as several other developments
were done as a part of the Google Summer of Code project.
Google provides financial support to students and organizations participating in the Google Summer of Code project.
\end{minipage}

@@

Attribute processing and queries in GRASS GIS can take an advantage of latest developments
in database management systems (DBMSs) as several DBMSs are supported most notably SQLite and PostgreSQL.
A PostGIS database can be connected including it geometry and topology.
In parallel to that native support the OGC Simple Features is available.

>>>>

\newlength{\grasslogoheight}
\setlength{\grasslogoheight}{0.09\textheight}
\newlength{\instlogoheight}
\setlength{\instlogoheight}{0.33\grasslogoheight}

\titlegraphic{
\begin{minipage}{0.3\linewidth}
\includegraphics[height=\grasslogoheight]{grass}
\hspace{2em}
\includegraphics[height=\grasslogoheight]{osgeo_project}
\end{minipage}
\hfill
\begin{minipage}{0.20\linewidth}
\setlength{\baselineskip}{120pt}
\begin{flushright}
\includegraphics[height=\instlogoheight]{ncstate}
~
\includegraphics[height=\instlogoheight]{ctu_prague}
~
\includegraphics[height=\instlogoheight]{dwd}
~
\includegraphics[height=\instlogoheight]{mundialis}
~
\includegraphics[height=\instlogoheight]{fem_cri}
~
\includegraphics[height=\instlogoheight]{iwmi}
~
\includegraphics[height=\instlogoheight]{ec_jrc}
~
\includegraphics[height=\instlogoheight]{eurac}
\end{flushright}
\end{minipage}
\vspace{-\grasslogoheight}
}

@@

\author{
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Yann Chemin\inst{2},
Martin Landa\inst{3},
Thomas Leppelt\inst{4},
Pietro Zambelli\inst{5},
Luca Delucchi\inst{6},
Margherita Di Leo\inst{7},
S\"{o}ren Gebbert,
and
Markus Neteler\inst{8}
}
\institute{
\large
\instlist{1}North Carolina State University, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu);
\instlist{2}IWMI, Sri Lanka;
\instlist{3}FCE CTU in Prague, Czech Republic;
\instlist{4}DWD, Germany;\\
\instlist{5}EURAC Research, Institute for Renewable Energy, Italy;
\instlist{6}Fondazione Edmund Mach, Research and Innovation Centre, Italy;
\instlist{7}European Commission, JRC, Italy;
\instlist{8}mundialis GmbH \& Co. KG, Germany;
}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{google}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
Initial development of \gmodule{i.segment} module as well as several other developments
were done as a part of the Google Summer of Code project.
Google provides financial support to students and organizations participating in the Google Summer of Code project.
\end{minipage}

@@

Attribute processing and queries in GRASS GIS can take an advantage of latest developments
in database management systems (DBMSs) as several DBMSs are supported most notably SQLite and PostgreSQL.
A PostGIS database can be connected including its geometry and topology.
In parallel to that native support the OGC Simple Features is available.
